Exploration of Financial Contributions to Presidential Campaigns in Texas by Jehyeon Heo.
========================================================

> **Tip**: You will see quoted sections like this throughout the template to
help you construct your report. Make sure that you remove these notes before
you finish and submit your project!

> **Tip**: One of the requirements of this project is that your code follows
good formatting techniques, including limiting your lines to 80 characters or
less. If you're using RStudio, go into Preferences \> Code \> Display to set up
a margin line to help you keep track of this guideline!

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(GGally)
library(scales)
library(memisc)
library(reshape2)
```

 Now I'm going to load the financial contributions by Texas data and candidates data.

```{r echo=FALSE, Load_the_datas}

# Load the financial data.
Data <- read.csv('ctrbsTX.csv',
                  row.names = NULL,
                  header = TRUE)

# Get header names without 'row.names'.
data_headers <- colnames(Data)[-1]

# In the data, remove the last column which is all NAs.
Data <- Data[,-19]

# Give the data right header names for each columns.
colnames(Data) <- data_headers

# Load the candidates data.
Cand <- read.csv('candidates.csv')

```

> **Tip**: Before you create any plots, it is a good idea to provide a short
introduction into the dataset that you are planning to explore. Replace this
quoted text with that general information!

 In 2016, there was presidential election in United States. At the result of it, Donald Trump became the 45th president of US. He gave sensational impact to Repulican party and became the nominee of it. His biggest rival was Hillary Clinton, Democratic party nominee. Lots of people forecasted that Hillary Clinton would win. But even if she got more votes than Trump in the election, she lost.
 
 In this document, I'm going to explore about financial contributions in Texas to presidential campaigns of 2016 US election. I chose Texas because I was interested in the state.
 
 I got the financial data from [FEC site](http://classic.fec.gov/disclosurep/pnational.do). And I also used the data about candidates. It has gender, party, height and age information of each candidates. I made the data by searching the internet.
 
 Before I enter into analysis, I'm going to introduce the questions that I got about the data.
 1. How was the distribution of the contributions? 
 2. How did the sum of contributions differ by parties or dates or candidates, etc?
 3. I want to know the results of above questions by comparing Hillary and Trump. And also for Republican party and Democratic party.
 4. Which contributer contributed the maximum amount? And who contributed most often?
 
 I'm sure that I'll get more questions as I explore the datas. I'll show you which questions I get when I explore the data and show the results of the exploration.
 
# Basic Data Exploration Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

 Fisrt, I'm going to explore financial data.
 
```{r echo=FALSE, Basic_Exploration_for_Data}

# Get the number of observations and columns.
dim(Data)

# Show the structure of the data.
str(Data)

# Show the distributions of the data by summary.
summary(Data)

# Get the number of candidates and columns.
print('Number of candidates in Data:')
length(unique(Data$cand_nm))

# Show some contributers' names.
print("Show top 5 most common contributers' names")
summary(Data$contbr_nm)[1:5]
```

 The Data has about 550,000 observations and 18 variables. And there are 25 candidates' information in it.
 
 And I can see from the structure and the summary of the Data that it would be difficult to identify unique contributers. If I try to sort out distinctive contributers by using names, there can be lots of different people with same name. Even if I try to use city or occupation variables too, I cannot know whether the contributions are made by diffrent people who live in the same city or by same person who moved to other city and changed his or her job. 
 
 I'm going to show the example below.
 
```{r echo=FALSE, same_name_different_people_example}

# Show the states of 'ROBINSON, ROBBIE'.
bonnie <- subset(Data, contbr_nm == 'RUDOLPH, BONNIE')

print("Show the states of 'RUDOLPH, BONNIE'.")

print('How many unique city names are registered for him?')
length(unique(bonnie$contbr_city))

print('What is the city names?')
unique(bonnie$contbr_city)

print('How many unique zip codes are registered for him?')
length(unique(bonnie$contbr_zip))

print('What is the zip codes?')
unique(bonnie$contbr_zip)

print('How many of people are registered as his employer?')
length(unique(bonnie$contbr_employer))

print('Who is his employer?')
unique(bonnie$contbr_employer)

print('How many occupations are registered for him?')
length(unique(bonnie$contbr_occupation))

print('What is his occupation?')
unique(bonnie$contbr_occupation)
```

 For example, in the data, it is written that RUDOLPH, BONNIE contributed 463 times. And it looked like he lives in Laredo, Texas. When I see the city name with zip codes and search about it using google, I think that Laredo is wrongly written to 'Latedo'.
 But when I see the employer and occupation of him, I cannot but have a question about the name's uniqueness. Is he retired? Or is he working at a university? Or did he work at a university and retired? I cannot know about it using only this data.
 Therefore I cannot answer the questions related with 'unique' contributers using this data.
 
 When I see the structure of Data, I found that the type of contb_receipt_dt should be date, not string. I'm going to change the type.
 
```{r echo=FALSE, from_string_to_date}

# Set locale of R.
print("Set locale as 'C'")
Sys.setlocale("LC_TIME", "C")

# Change the type to Date.
Data$contb_receipt_dt <- as.Date(
  Data$contb_receipt_dt, '%d-%b-%y'
)

# Check the result using str function.
str(Data$contb_receipt_dt)

```

 contb_receipt_dt types of values are changed to date.
 
 Now I'm going to explore candidates data, too.

```{r echo=FALSE, Basic_exploration_for_Cand}

# Get the number of observations and columns.
dim(Cand)

# Show the structure of the data.
str(Cand)

# Show the distributions of the data by summary.
summary(Cand)

# Show whether the unique values of the candidates' names are all equal to the cand's X values.
print("If the unique values of the candidates' names in Data are all equal to the values in cand:")

all(unique(Data$cand_nm) == Cand$X)

```

 There are 25 candidates' information in Cand. 17 of them are included in Repulican party and 5 of them are in Democratic party. And only 3 of all candidates are female.

 I think that it is good to add new column which notify who became presidential nominee from each party. I'm going to name the column as 'if_nominee' and assign TRUE for nominees and FALSE for others. And I'm going to regard Evan McMullin, independent presidential candidate as a nominee.

```{r echo=FALSE, make_if_nominee_column}

nominees = c('Clinton, Hillary Rodham', 
             'Trump, Donald J.',
             'Johnson, Gary',
             'McMullin, Evan',
             'Stein, Jill')

Cand$if_nominee <- ifelse(Cand$cand_nm %in% nominees, TRUE, FALSE)

summary(Cand$if_nominee)
```

 5 candidates became nominees and others couldn't(or didn't).

 When I explored the candidates' data, I found that the values of the candidates' names are same for Data and Cand that I can merge Data and Cand by outer join using 'cand_nm' column. I'm going to use only 'cand_nm', 'cand_party' and 'if_nominee' columns to join.

```{r echo=FALSE, outer_join_Data_and_Cand}

# Merge the 'Data' and 'Cand' by outer join.
Data <- merge(x = Data, 
              y = Cand[,c('cand_nm', 'cand_party', 'if_nominee')],
              by = 'cand_nm',
              all.x = TRUE)

str(Data)
```

 I can see that 'cand_party' and 'if_nominee' columns are added to Data.

# Univariate Plots Section

 Now I'm going to get univariate plots.
 
```{r echo=FALSE, Univariate_cand_nm_counts}

# First, I'm going to show the distribution of the count of contributions for each candidates.
name_counts <- as.data.frame(sort(table(Data$cand_nm, dnn = 'name'),
                                  decreasing = T),
                             responseName = 'count')

name_counts

# Show the counts.
ggplot(aes(x = name, y = count),
       data = name_counts) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Show the percentages.
ggplot(aes(x = name, y = count/sum(count)),
       data = name_counts) +
  geom_bar(stat = 'identity') +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```

  Clinton got the most number of contributions. After her, Cruz, Sanders, Trump, Carson, etc. follow. When change the counts to percentages, Clinton got about 38% and Cruz, Sanders, Trump and Carson followed by about 25%, 15%, 14%, 5% each.

```{r echo=FALSE, Univariate_city_counts}

# I'm going to show the distribution of the count of contributers in each cities in Texas.

# Get count of contributions by cities.
cities_counts <- as.data.frame(sort(table(Data$contbr_city, dnn = 'name'),
                                    decreasing = T),
                               responseName = 'count')

# Show the number of cities.
length(cities_counts$name)

# Show the counts of top10.
ggplot(aes(x = name, y = count),
       data = cities_counts[1:10, ]) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```

 There are 2252 city names in the data that I showed top 10 results.
 
 The top 10 cities of Texas by population ordered by rank are Houston, San Antonio, Dallas, Austin, Fort Worth, El paso, Arlington, Corpus Christi, Plano and Laredo. But when I see the top 10 counts by contributions, the rank is a little different from the rank by population. San Antonio changed the rank with Austin. And while Corpus Christi and Laredo are inclued in populated top 10, they didn't appear at top 10 counts.
 
```{r echo=FALSE, Univariate_contribution_amount}

# I'm going to show the distribution of contribution amounts in Texas.
summary(Data$contb_receipt_amt)

head(sort(table(Data$contb_receipt_amt), decreasing = T))

# Show the histogram. I designated binwidth as 100$.
ggplot(aes(x = contb_receipt_amt),
       data = Data) +
  geom_histogram(binwidth = 100) +
  scale_x_continuous(breaks = seq(-15000, 15000, 5000))
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Show the histogram for center 50% of amounts. I designated binwidth as 1$.
ggplot(aes(x = contb_receipt_amt),
       data = subset(Data,
                     contb_receipt_amt >= quantile(Data$contb_receipt_amt, 0.25) & contb_receipt_amt <= quantile(Data$contb_receipt_amt, 0.75))) +
  geom_histogram(binwidth = 1) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  scale_x_continuous(limits = c(15, 105))

```
 
 The minimum and maximum amount was -16600\$ and 15,000$ each. It is weird that there are - values of contributions. I need to find what causes it.
 
 The most common contribution amount is 25\$. 50\$, 100\$ follow it. It is unexpected to see that 25$ is the most common one because I thought that it is convenient to contribute an amount in the tens.
 
 I can see from the table and histogram that most of contributions are in between 20\$ and 100$.
 
```{r echo=FALSE, Univariate_contribution_date_counts}

# I'm going to show the distribution of contributions' dates in Texas.

# Get count of contributions by dates.
dates_counts <- as.data.frame(table(Data$contb_receipt_dt, dnn = 'date'),
                              responseName = 'count')

dates_counts$date <- as.Date(dates_counts$date, format = '%Y-%m-%d')

# Show the top 6 dates of counts.
head(dates_counts[order(-dates_counts$count),])

# Show the counts for each date by line graph.
# I chose line graph this time because I thought that it is the right method to express time series data.
ggplot(aes(x = date, y = count),
       data = dates_counts) +
  geom_line() +
  scale_x_date() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

# Show the counts for each month by line graph.
ggplot(aes(x = substr(date, 1, 7), y = count, group = 1),
       data = dates_counts) +
  geom_line(stat = 'summary',
           fun.y = sum) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))
```

 When I see the top 6 dates of counts, there were the most contributions in July 11th, and 12th of 2016.
 
 And I can see that the overall contribution counts are increased from March, 2015 to March, 2016. And then it decreased and increased 2 times peaking at July, 2016 and October, 2016. It is overall trend and I can see from the line graph for each date that there are really lots of and huge fluctuations.
 
```{r echo=FALSE, univariate_election_type_counts}

# I'm going to show the distribution of contributions for election types in Texas.

# Get counts of contributions by election types.
election_types_counts <- as.data.frame(table(Data$election_tp, dnn = 'type'),
                                       responseName = 'count')

# Show the counts.
election_types_counts[order(-election_types_counts$count),]

ggplot(aes(x = type, y = count),
       data = election_types_counts) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```

 Most of contributions are for P2016 and G2016. US Presidential elections are divided into 2 stages, primary and general. Therefore I think that it is right because this data is about the financial contributions for presidential eletion. 
 But there are some contributions whose election types, to my thinking, aren't related with it. I'm going to investigate deeply about them in the following.

```{r echo=FALSE, consider_election_types_other_than_P2016_and_G2016}

# Show the data whose election type is O2016.
print('Head and tail parts of datas whose election type is O2016')
O2016 = subset(Data, election_tp == 'O2016')
head(O2016)
tail(O2016)

print('Are all O2016 contributions for Jill Stein?')
all(O2016$cand_nm == 'Stein, Jill')

print('Since When and till when the contributions are received?')
range(O2016$contb_receipt_dt)

# Show the data whose election type is P2012.
print('Datas whose election type is P2012')
subset(Data, election_tp == 'P2012')

# Show the data whose election type is ''. 
# I'm going to print head and tail of the data because there are more 1500 rows.
print("Head and tail parts of datas whose election type is ''")
election_type_vacant <- subset(Data, election_tp == '')
head(election_type_vacant)
tail(election_type_vacant)

print('Who is for the contributions?')
unique(election_type_vacant$cand_nm)

print('Since when and till when the nominees received them?')
election_type_vacant %>%
  filter(if_nominee) %>%
  group_by(cand_nm) %>%
  summarise(start_date = min(contb_receipt_dt),
            end_date = max(contb_receipt_dt)) %>%
  arrange(start_date)

# I chose line graph to show trend as time goes on.
ggplot(aes(x = contb_receipt_dt, y = ..count..), 
       data = subset(election_type_vacant, 
                     if_nominee == T)) + 
  geom_freqpoly(aes(color = cand_nm)) + 
  scale_x_date(date_breaks = '1 month') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

print("When candidates who aren't nominees received them?")
range(subset(election_type_vacant, if_nominee == F)$contb_receipt_dt)

ggplot(aes(x = contb_receipt_dt, y = ..count..), 
       data = subset(election_type_vacant, 
                     if_nominee == F)) + 
  geom_freqpoly() + 
  scale_x_date(date_breaks = '1 month') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```

 First, when I see the head and tail parts about datas whose type is O2016, it looked like they are all for Jill Stein. Thus, I checked whether the contributions are all for her and it was.

 Jill Stein was Green party nominee that I want to know since when and till when the contributions are given. And I found that they are from 2016-11-23 to 2016-11-28. It is after the election. And compared to the all election times it is really short.

 I searched about her and I found that it is related with [presidential election recount fundraising](https://en.wikipedia.org/wiki/Jill_Stein#2016). This is why they were classified as O2016, 'other' type election in 2016. It is not related with primary or general election. Therefore I think that it is better to exclude O2016 when exploring the data.
 
 
 Second, I got the datas whose type is P2012. I really wondered why the contributions related with 2012 election are in here. 
 
 There are only 2 contributions and I searched about ['Gunn, George'](https://www.fec.gov/data/receipts/individual-contributions/?two_year_transaction_period=2016&contributor_name=Gunn%2C+george&min_date=01%2F01%2F2015&max_date=12%2F31%2F2016&contributor_employer=HSI) and ['Wylie, Wayne'](https://www.fec.gov/data/receipts/individual-contributions/?two_year_transaction_period=2016&contributor_name=wylie%2C+wayne&min_date=01%2F01%2F2015&max_date=12%2F31%2F2016&contributor_employer=jpmorgan+chase) in FEC site. And I found that they did them to 'Rick Santorum for president, inc.(2012)'. Even though they contributed in 2015 and 2016, it looked like they did them for debt retirement for [Rick Santorum's 2012 US president election](https://en.wikipedia.org/wiki/Republican_Party_presidential_primaries,_2012). Therefore I think that the contributions are not for Santorum's 2016 election and exclude P2012 when exploring the data.
 
 Third, when I see the head and tail parts about datas whose type is '', it looked like they are all for several candidates. Thus, I checked who received the contributions and 11 candidates got them.
 
 In the 11 candidates, there were nominees and those who aren't. Therefore I thought that it is good to investigate the data dividing by if_nominee variable.
 
 When I got the contributions' start date and end date for each nominees, I found that Jill Stein got them even when she didn't begin her campaign. And Trump and McMullin got them when they are running campaigns for general election. I can find about the fact in the line graph, too. It made me think that it is better to assign the type of contributions for Trump and McMullin to G2016 and other the type of the contributions for others including Stein to P2016.
 
 I found that it can be applied to candidates who weren't nominees by drawing the line graph for them. The contributions for them almost stopped from July, 2016. July, 2016 was the month that [Republican](https://en.wikipedia.org/wiki/Republican_Party_presidential_primaries,_2016) and [Democratic](https://en.wikipedia.org/wiki/Democratic_Party_presidential_primaries,_2016) presidential primaries took place.
 
 But to be more confident to my thinking for assigning types, I searched for contributers whose names appear in the head and tail part of election_type_vacant in [FEC site](https://www.fec.gov/data/receipts/individual-contributions/?two_year_transaction_period=2016&min_date=01%2F01%2F2015&max_date=12%2F31%2F2016). 
 
 Refunded contributions didn't appear in the site. Some contributions are recorded as primary(one example in [here](https://www.fec.gov/data/receipts/individual-contributions/?two_year_transaction_period=2016&contributor_name=WAY%2C+RICHARD+A+MR.&min_date=01%2F01%2F2015&max_date=12%2F31%2F2016) 2016-08-26 data) instead of ''. And others are recorded '' as it is in Data. 
 
 I also found [FEC contribution brochure site](https://transition.fec.gov/pages/brochures/contrib.shtml) that there can be presumptive redesignations for 'Is not designated in writing for a particular election;' cases. 

 Therefore I decided to leave the election type '' as it is. And I'll also use the data of the type too distinguishing from P2016 and G2016. I think that it is the case of not designating for a particular election in writing the contribution form.


> **Tip**: Make sure that you leave a blank line between the start / end of
each code block and the end / start of your Markdown text so that it is
formatted nicely in the knitted text. Note as well that text on consecutive
lines is treated as a single space. Make sure you have a blank line between
your paragraphs so that they too are formatted for easy readability.


# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

print('How contribution receipt dates for Trump and McMullin are different for P2016 and G2016 each?')

ggplot(aes(x = contb_receipt_dt, y = ..count..),
       data = subset(Data, 
                     cand_nm %in% c('Trump, Donald J.', 'McMullin, Evan') & election_tp %in% c('P2016', 'G2016'))) +
  facet_wrap(~cand_nm, scales = 'free_y', nrow = 2, dir = 'v') +
  geom_freqpoly(aes(color = election_tp))

print("How contribution receipt dates for those who aren't nominees are different for P2016 and G2016 each?")

ggplot(aes(x = contb_receipt_dt, y = ..count..),
       data = subset(Data, 
                     !if_nominee & election_tp %in% c('P2016', 'G2016'))) +
  geom_freqpoly(aes(color = election_tp)) +
  scale_x_date(date_breaks = '3 month') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5))

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!