Exploration of Financial Contributions to Presidential Campaigns in Texas by Jehyeon Heo.
========================================================

> **Tip**: You will see quoted sections like this throughout the template to
help you construct your report. Make sure that you remove these notes before
you finish and submit your project!

> **Tip**: One of the requirements of this project is that your code follows
good formatting techniques, including limiting your lines to 80 characters or
less. If you're using RStudio, go into Preferences \> Code \> Display to set up
a margin line to help you keep track of this guideline!

```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using in your analysis in this code
# chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk. This
# prevents the code from displaying in the knitted HTML output. You should set
# echo=FALSE for all code chunks in your file, unless it makes sense for your
# report to show the code that generated a particular plot.

# The other parameters for "message" and "warning" should also be set to FALSE
# for other code chunks once you have verified that each plot comes out as you
# want it to. This will clean up the flow of your report.

library(ggplot2)
library(dplyr)
library(RColorBrewer)
library(GGally)
library(scales)
library(memisc)
library(reshape2)
```

```{r echo=FALSE, Load_the_Data}

# Load the main data.
Data <- read.csv('ctrbsTX.csv',
                  row.names = NULL,
                  header = TRUE)

# Get header names without 'row.names'.
data_headers <- colnames(Data)[-1]

# In the data, remove the last column which is all NAs.
Data <- Data[,-19]

# Give the data right header names for each columns.
colnames(Data) <- data_headers

# Load the data about candidates.
cand <- read.csv('candidates.csv')

# Merge the 'Data' and 'cand' by left join.
Data <- merge(x = Data, 
              y = cand,
              by.x = 'cand_nm',
              by.y = 'X',
              all.x = TRUE)
```

> **Tip**: Before you create any plots, it is a good idea to provide a short
introduction into the dataset that you are planning to explore. Replace this
quoted text with that general information!

 In 2016, there was presidential election in United States. At the result of it, Donald Trump became the 45th president of US. He gave sensational impact to Repulican party and became the nominee of it. His biggest rival was Hillary Clinton, Democratic party nominee. Lots of people forecasted that Hillary Clinton would win. But even if she got more votes than Trump in the election, she lost.
 
 In this document, I'm going to explore about financial contributions in Texas to presidential campaigns of 2016 US election. I chose Texas because I was interested in the state.
 
 I got the financial data from [FEC site](http://classic.fec.gov/disclosurep/pnational.do). And I also used the data about candidates. It has gender, party, height and age information of each candidates. I made the data by searching the internet.
 
 Before I enter into analysis, I'm going to introduce the questions that I got about the data.
 1. How was the distribution of the contributions? 
 2. How did the sum of contributions differ by parties or dates or candidates, etc?
 3. I want to know the results of above questions by comparing Hillary and Trump. And also for Republican party and Democratic party.
 4. Which contributer contributed the maximum amount? And who contributed most often?
 
 I'm sure that I'll get more questions as I explore the datas. I'll show you which questions I get when I explore the data and show the results of the exploration.
 
# Univariate Plots Section

> **Tip**: In this section, you should perform some preliminary exploration of
your dataset. Run some summaries of the data and create univariate plots to
understand the structure of the individual variables in your dataset. Don't
forget to add a comment after each plot or closely-related group of plots!
There should be multiple code chunks and text sections; the first one below is
just to help you get started.

```{r echo=FALSE, Basic_Exploration}

# Get the number of observations and columns.
dim(Data)

# Show the structure of the data.
str(Data)

# Show the distributions of the data by summary.
summary(Data)

# Get the number of candidates and columns.
length(unique(Data$cand_nm))

# Show whether the unique values of the candidates' names are all equal to the cand's X values.
print("If the unique values of the candidates' names in Data are all equal to the values in cand:")

all(unique(Data$cand_nm) == cand$X)

# Show the distributions of the candidates information by summary.
summary(cand)
```

 Merged data has about 550,000 observations and 22 variables. And there are 25 candidates' information in the data. The values of the candidates' names are same for Data and cand that that I could show the information about the candidates in Data by using the summary function to cand.
 When I see the structure of the data, I found that the type of contb_receipt_dt should be date, not string. I'm going to change the type.
 
```{r echo=FALSE, from_string_to_date}

Sys.setlocale("LC_TIME", "C")

Data$contb_receipt_dt <- as.Date(
  Data$contb_receipt_dt, '%d-%b-%y'
)

str(Data$contb_receipt_dt)
```

 contb_receipt_dt types of values are changed to date.

 Now I'm going to get univariate plots.
 
```{r echo=FALSE, Univariate_cand_nm_counts}

# First, I'm going to show the distribution of the count of contributions for each candidates.
name_counts <- as.data.frame(sort(table(Data$cand_nm, dnn = 'name'),
                                  decreasing = T),
                             responseName = 'count')

name_counts

# Show the counts.
ggplot(aes(x = name, y = count),
       data = name_counts) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Show the percentages.
ggplot(aes(x = name, y = count/sum(count)),
       data = name_counts) +
  geom_bar(stat = 'identity') +
  scale_y_continuous(labels = percent_format()) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

  Clinton got the most number of contributions. After her, Cruz, Sanders, Trump, Carson, etc. follow. When change the counts to percentages, Clinton got about 38% and Cruz, Sanders, Trump and Carson followed by about 25%, 15%, 14%, 5% each.

```{r echo=FALSE, Univariate_city_counts}

# I'm going to show the distribution of the count of contributers in each cities in Texas.

# Get count of contributions by cities.
cities_counts <- as.data.frame(sort(table(Data$contbr_city, dnn = 'name'),
                                    decreasing = T),
                               responseName = 'count')

# Show the number of cities.
length(cities_counts$name)

# Show the counts of top10.
ggplot(aes(x = name, y = count),
       data = cities_counts[1:10, ]) +
  geom_bar(stat = 'identity') +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

```

 There are 2252 city names in the data that I showed top 10 result.
 The top 10 cities of Texas by population are Houston, San Antonio, Dallas, Austin, Fort Worth, El paso, Arlington, Corpus Christi, Plano and Laredo ordered by rank. But when I see the counts by top 10 count of contributers' cities, the rank is a little different from the former rank. San Antonio changed the rank with Austin. And Corpus Christi and Laredo didn't appear at top 10 count, while they are inclued in populated top 10.
 I got counts of contributions by each cities. This makes me wonder whether there are some contributers who contributed more than once. If if is true, it would be worth trying to get the distribution of the cities by unique contributers, not by count. 
 
> **Tip**: Make sure that you leave a blank line between the start / end of
each code block and the end / start of your Markdown text so that it is
formatted nicely in the knitted text. Note as well that text on consecutive
lines is treated as a single space. Make sure you have a blank line between
your paragraphs so that they too are formatted for easy readability.

# Univariate Analysis

> **Tip**: Now that you've completed your univariate explorations, it's time to
reflect on and summarize what you've found. Use the questions below to help you
gather your observations and add your own if you have other thoughts!

### What is the structure of your dataset?

### What is/are the main feature(s) of interest in your dataset?

### What other features in the dataset do you think will help support your \
investigation into your feature(s) of interest?

### Did you create any new variables from existing variables in the dataset?

### Of the features you investigated, were there any unusual distributions? \
Did you perform any operations on the data to tidy, adjust, or change the form \
of the data? If so, why did you do this?


# Bivariate Plots Section

> **Tip**: Based on what you saw in the univariate plots, what relationships
between variables might be interesting to look at in this section? Don't limit
yourself to relationships between a main output feature and one of the
supporting variables. Try to look at relationships between supporting variables
as well.

```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

> **Tip**: As before, summarize what you found in your bivariate explorations
here. Use the questions below to guide your discussion.

### Talk about some of the relationships you observed in this part of the \
investigation. How did the feature(s) of interest vary with other features in \
the dataset?

### Did you observe any interesting relationships between the other features \
(not the main feature(s) of interest)?

### What was the strongest relationship you found?


# Multivariate Plots Section

> **Tip**: Now it's time to put everything together. Based on what you found in
the bivariate plots section, create a few multivariate plots to investigate
more complex interactions between variables. Make sure that the plots that you
create here are justified by the plots you explored in the previous section. If
you plan on creating any mathematical models, this is the section where you
will do that.

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the \
investigation. Were there features that strengthened each other in terms of \
looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the \
strengths and limitations of your model.

------

# Final Plots and Summary

> **Tip**: You've done a lot of exploration and have built up an understanding
of the structure of and relationships between the variables in your dataset.
Here, you will select three plots from all of your previous exploration to
present here as a summary of some of your most interesting findings. Make sure
that you have refined your selected plots for good titling, axis labels (with
units), and good aesthetic choices (e.g. color, transparency). After each plot,
make sure you justify why you chose each plot by describing what it shows.

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection

> **Tip**: Here's the final step! Reflect on the exploration you performed and
the insights you found. What were some of the struggles that you went through?
What went well? What was surprising? Make sure you include an insight into
future work that could be done with the dataset.

> **Tip**: Don't forget to remove this, and the other **Tip** sections before
saving your final work and knitting the final report!